Hydra battles in Coq

### 2020-09-24 doc/hydras.tex
minor simplifications
merge omegaomega into master
better name consistency in selectors of types ON and SubON

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, Bordeaux-INP\\with contributions by \'Evelyne Contejean and Florian Hatat}
\date{\today}
\title{Hydra battles in Coq}
\makeindex
\begin{document}
\maketitle

@@

Definition on_compare {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : ON lt compare} := compare.

Definition on_lt {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} := lt.
Infix "o<" := on_lt : ON_scope.

Definition on_le  {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} :=
  clos_refl _ on_lt.

Infix "o<=" := on_le : ON_scope.
\end{Coqsrc}

@@

\begin{figure}[h]
   \centering
   \begin{tikzpicture}[very thick, scale=0.5]
\begin{scope}[color=blue]
\node(A0) at (2,0)[label=below:$0$]{$\bullet$};
\node(A1) at (3,0)[label=below:$1$]{$\bullet$};
\node(A2) at (4,0)[label=below:$2$]{$\bullet$};
\node (Adots) at (6,0) {$\ldots$};
\node(An) at (8,0)[label=below:$n$]{$\bullet$};
\node(A2) at (10,0)[label=below:$n+1$]{$\bullet$};
\node (Adots1) at (12,0) {$\ldots$};
\end{scope}
\begin{scope}[color=red]
\node(B0) at (14,0)[label=below:$0$,label=above:$\omega$]{$\bullet$};
\node(B1) at (16,0)[label=below:$1$, label=above:$\omega+1$]{$\bullet$};
\node(B2) at (18,0)[label=below:$2$,label=above:$\omega+2$]{$\bullet$};
\node (Bdots) at (20,0) {$\ldots$};
\node (Bn) at (22,0) [label=below:$p$, label=above:$\omega+p$]{$\bullet$};
\node (Bdots2) at (24,0) {$\ldots$};
\end{scope}
\end{tikzpicture}
   \caption{\textcolor{blue}{$\omega+{\color{red}\omega}$}}
   \label{fig:omega-plus-omega}
 \end{figure}

@@

Thus, $m(\iota(p)) > (i,j)$ for any $j$.
Applying the lemma \texttt{limit\_is\_lub}, we get  the inequality
$\iota(i+1,0)\geq (i+1,0)$

@@

\begin{Coqsrc}
Class  SubON 
       `(OA : @ON A ltA  compareA)
       `(OB : @ON B ltB  compareB)
       (alpha :  B)
       (iota : A -> B):=
  {
  subon_compare: forall x y : A,  compareB (iota x) (iota y) =
                                 compareA x y;
  subon_incl : forall x, ltB (iota x) alpha;
  subon_onto : forall y, ltB y alpha  -> exists x:A, iota x = y}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Instance Zero : E0.
Proof.
  refine (@mkord T1.zero _);  now compute. 
Defined.

Instance _Omega : E0.
Proof.  now exists omega. Defined.

>>>>

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, Bordeaux-INP\\with contributions by \'Evelyne Contejean,  Florian Hatat and Pascal Manoury}
\date{\today}
\title{Hydra battles in Coq}
\makeindex
\begin{document}
\maketitle

@@

Definition ON_compare {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : ON lt compare} := compare.

Definition ON_lt {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} := lt.
Infix "o<" := ON_lt : ON_scope.

Definition ON_le  {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} :=
  clos_refl _ ON_lt.

Infix "o<=" := ON_le : ON_scope.
\end{Coqsrc}

@@

\begin{figure}[h]
   \centering
   \begin{tikzpicture}[very thick, scale=0.5]
\begin{scope}[color=blue]
\node(A0) at (2,0)[label=below:$0$]{$\bullet$};
\node(A1) at (3,0)[label=below:$1$]{$\bullet$};
\node(A2) at (4,0)[label=below:$2$]{$\bullet$};
\node (Adots) at (6,0) {$\ldots$};
\node(An) at (8,0)[label=below:$n$]{$\bullet$};
\node(A2) at (10,0)[label=below:$n+1$]{$\bullet$};
\node (Adots1) at (12,0) {$\ldots$};
\end{scope}
\begin{scope}[color=red]
\node(B0) at (14,0)[label=below:$0$,label=above:\textcolor{red}{$\omega$}]{$\bullet$};
\node(B1) at (16,0)[label=below:$1$, label=above:$\omega+1$]{$\bullet$};
\node(B2) at (18,0)[label=below:$2$,label=above:$\omega+2$]{$\bullet$};
\node (Bdots) at (20,0) {$\ldots$};
\node (Bn) at (22,0) [label=below:$p$, label=above:$\omega+p$]{$\bullet$};
\node (Bdots2) at (24,0) {$\ldots$};
\end{scope}
\end{tikzpicture}
   \caption{\textcolor{blue}{$\omega+{\color{red}\omega}$}}
   \label{fig:omega-plus-omega}
 \end{figure}

@@

Thus, $m(\iota(p)) > (i,j)$ for any $j$.
Applying the lemma \texttt{limit\_is\_lub}, we get  the inequality
$m(\iota(i+1,0))\geq (i+1,0)$

@@

\begin{Coqsrc}
Class  SubON 
       `(OA : @ON A ltA  compareA)
       `(OB : @ON B ltB  compareB)
       (alpha :  B)
       (iota : A -> B):=
  {
  SubON_compare: forall x y : A,  compareB (iota x) (iota y) =
                                 compareA x y;
  SubON_incl : forall x, ltB (iota x) alpha;
  SubON_onto : forall y, ltB y alpha  -> exists x:A, iota x = y}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Instance Zero : E0.
Proof.
  now exists T1.zero.
Defined.

Instance _Omega : E0.
Proof.  now exists omega%t1. 
Defined.
